Adaption of the Chumbley Score to matching of bullet striation marks

### 2017-10-01 doc/paper.Rmd
failed tests included

```{r}
ns <- all %>% group_by(wv, wo, match) %>% summarize(
  n_ss = mean(same_shift_n),
  n_ds = mean(diff_shift_n),
  miss = sum(is.na(p_value))
)
ns %>% filter(wv %in% c(30, 50)) %>% 
  ggplot(aes(x = match, y = n_ds, shape=match, colour = factor(wv))) + 
  geom_point() + geom_line(aes(group=wv)) + facet_wrap(~wo)
```

>>>>

```{r, fig.width=8, fig.height=5, fig.cap="Number of failed tests."}
ns <- all %>% group_by(wv, wo, match) %>% summarize(
  n_ss = mean(same_shift_n),
  n_ds = mean(diff_shift_n),
  zero_ss = sum(same_shift_n==0),
  zero_ds = sum(diff_shift_n==0),
  miss = sum(is.na(p_value))
)
ns %>% filter(wv %in% c(30, 50)) %>% 
  ggplot(aes(x = wo, y = miss, shape=factor(wv), colour = factor(match))) + 
  geom_point() + 
  theme_bw() +
  ylab("Number of failed tests.")
```
